
Twitter is an emerging microblog service provider from 2006. Twitter users can add hashtags to label and classify their posts. But, only about $11\%$ tweets contain at least one hashtag. Thus, hashtag prediction for any tweet texts is a necessary task for tweets analysis. 

At the same time, the tweets also become a 

 From 2012, neural network and deep learning models have been successfully applied into different areas of computer vision, speech recognition and natural language processing (NLP). Recurrent Neural Network (RNN) is one type of neural network model which utilizes the sequential information during training process. RNN models can classify the data in high performance. But they are black-boxes. It is challenge to explore what information a RNN model learns and stores in its hidden states.  
 
 Visual analytics and relevant interaction techniques are potential to assist to understand RNN models. However, how to design efficient and usable visual representations of RNN hidden states with necessary interactions to aid sensemaking is still challenging.

To address this, my thesis work highlights three contributions: \\

 We designed a RNN based visual analytics system for rumor tweets analysis in hashtag prediction, tweets clustering, and interactive visualization.\\

%Our interactive visualization design is based on the pre-survey of the professional journalists and 

%However, other study is most based on the single event, like Boston bombing. Thus, our research conclusions can be 
%This design would be more general to apply to the normal  prediction and application. 


%When this happens, a new scarce resource, {}, emerges. 
%Over time, the company that makes all the money is the one who gains a monopoly hold on {} and become the only game in town.

% format for the motivation and abstract. 
%In current industry ______, customers are over-served by _______: they spend too much of their time, money, or other on _______, and it feels inefficient, saturated or wasteful. The real reason they’re served by ______ in the first place is because they have a higher level need, _______. Unfortunately, it’s difficult to serve these customers at this level directly because of some constraint, ________, which is often difficult to recognize.
%However, that constraint melts away when _________ becomes abstracted away into something scalable and abundant because of _______. When this happens, _______ can now serve customers directly at their higher level need, _______, by leveraging the abundant element _______ in brand new ways that never existed before. When this happens, a new scarce resource, _______, emerges. Over time, the company that makes all the money is the one who gains a monopoly hold on ______ and become the only game in town.